---
title: "R-Lady branded presentation"
author: 'One R-Lady'
date: '`r Sys.Date()`'

output: 
  revealjs::revealjs_presentation:
    css: rladies_revealjs.css
    highlight: pygments
    transition: slide
    
---
```{r}
# R-Ladies ggplot2 theme from Samantha Tyner

r_ladies_theme <- function(base_size){
  theme_bw(base_size) %+replace% 
    theme(text = element_text(family = "HelveticaNeue", face = "plain", size = base_size,
                              colour = 'black',
                              hjust = .5, vjust = .5, angle = 0, 
                              lineheight = 1.1, 
                              margin = margin(t = 0, r = 0, b = 0, l = 0, 
                                              unit = "pt"), 
                              debug= FALSE), 
          axis.text = element_text(colour = "#181818"), 
          axis.title = element_text(face = "bold", colour = "#88398A", size = rel(1.1)), 
          plot.title = element_text(face = "bold", size = rel(1.4), 
                                    colour = "#88398A", 
                                    margin = margin(t = 0, r = 0, b = 6.6,
                                                    l = 0, unit = "pt")),
          legend.title = element_text(face = "bold", colour = "#181818"),
          panel.grid.major = element_line(color = "#D3D3D3"))
}

library("ggplot2")
theme_set(r_ladies_theme(base_size = 18))
```
## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE, warning = FALSE, message = FALSE}

ggplot(cars) +
  geom_point(aes(speed, dist)) +
  ggtitle("Our pretty plot")
```

